Proportional multi-state multiple-cohort life table model

### 2018-05-09 MSLT/MSLTdoc.Rmd
Loop graphs

          index <- index + 1
        }

@@

## ADD LOOP
disease_outcome <- "Incidence of Ischemic Heart Disease"

>>>>

          index <- index + 1
    }
  }
}

@@

#### Test code with loops for aggregated outcomes diseases burden. NOT WORKING.

### Compare with loops for age and sex cohort outcomes.

p_aggr_list <- list()
index <- 1

p_aggr_list_index <- ggplot(total_aggr[1:79,], aes(x = sim_year)) +

  geom_line(mapping = aes(y = paste("total", outcome, "num_bl", disease, sep = "_"), colour = paste("total", outcome, "num_bl", disease, sep = "_"))) +
  theme_classic() +
  geom_hline(yintercept=0, linetype="dashed", color = "black") +
  geom_line(mapping = aes(y = paste("total", outcome, "num_sc", disease, sep = "_"), colour = paste("total", outcome, "num_sc", disease, sep = "_"))) +
  geom_line(mapping = aes(y = paste("total", outcome, "num_dif", disease, sep = "_"), colour = paste("total", outcome, "num_diff", disease, sep = "_"))) +
  xlab ("Simulation years") + ylab ("Cases") + labs (title = paste(disease)) +
  theme(plot.title = element_text(hjust = 0.5, size = 12)) +
  scale_color_discrete(name = paste(""), labels = c("Baseline", "Difference", "Scenario")) +
  theme(plot.title = element_text(hjust = 0.5))
p_aggr_list[[index]] <- p_aggr_list_index  
index <- index + 1

#####
## original code with single outcomes
disease_outcome <- "Incidence of Ischemic Heart Disease"
